Timbral similarity between extended playing techniques: the next frontier in querying instrumental databases

### 2018-01-28 paper/lagrangeSpontaneousSimilarity2017.tex
comment on citing Siedenburg et al.

\vl{On pairwise similarity judgments of timbre, cite:
McAdams, S et al. (1995). Perceptual scaling of synthesized musical
timbres: common dimensions, specificities, and latent subject
classes. In: Psychological research 58.3, pp. 177-192}

@@

>>>>

\vl{On pairwise similarity judgments of timbre, cite:
McAdams, S et al. (1995). Perceptual scaling of synthesized musical
timbres: common dimensions, specificities, and latent subject
classes. In: Psychological research 58.3, pp. 177-192.
@biblio}

@@

\vl{On the importance of spectrotemporal modulations in the description
of timbre, and the commonalities and differences between the notions of
"feature" in music signal processing and music psychology:
Siedenburg, Fujinaga, and McAdams. "A comparison of
approaches to timbre descriptors in music information retrieval
and music psychology." In: Journal of New Music Research 45.1,
pp. 27?41. @biblio}
